---
title: "Assignment-slides"
author: "Jenny"
date: "5/29/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Application Function
This shiny application provides the user with plots of MPG(Miles/(US) gallon) against different variables. 

The Application contains :

**Left Pane** : 

- Select Variable from Dataset

**Main Panel** : 

- Summary : This displays summary for the data as per user selection
- Structure : This displays Strucutre for the data as per user selection
- Data : This displays data frame for the user selected options
- Plot : This displays plot for corresponding dataframe

## First Objective:
Shiny Application: [Link](https://jennyxu93.shinyapps.io/dataProductsAssignment/)

Github Repository: [Link](https://github.com/XiaoJenJen/data-products)

## Second Objective:
The Presentation is available at Rpubs:
[Link](http://rpubs.com/JenJen/392923)

## Dataset
The data used in the app comes from the Motor Trend Car Road Tests (mtcars) dataset. 
```{r,echo=TRUE}
summary(mtcars)
```

